---
title: "p8105_hw6_hb2699"
author: "Han Bao"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(purrr)
library(modelr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "right"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```
## Problem 2 

```{r, warning=FALSE, message=FALSE}
# Import the dataset
homicide_raw <- read_csv(url("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"), na = c("", "NA", "Unknown"))
# Clean dataset and Create variables city_state, resolved;Omit cities without victim race reports and error city;Limit victim_race to white or black
homicide_df = homicide_raw %>% 
  janitor::clean_names() %>%
  mutate(reported_date = as.Date(as.character(reported_date), format = "%Y%m%d"),
         victim_age = as.numeric(victim_age),
         victim_race = fct_relevel(victim_race, "White"),
         city_state = str_c(city, state, sep = ", "),
         resolved = case_when(
           disposition == "Closed without arrest" ~ 0,
           disposition == "Open/No arrest" ~ 0,
           disposition == "Closed by arrest" ~ 1)) %>% 
  relocate(city_state) %>% 
  filter(!city_state %in% c("Dallas, TX","Phoenix, AZ","Kansas City, MO","Tulsa, AL"),
         victim_race %in% c("White","Black"))
```
```{r, warning=FALSE, message=FALSE}
#  In Baltimore, MD, fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors.And Obtain the estimate and CI of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.
baltimore_logistic = homicide_df %>%
    filter(city_state == "Baltimore, MD") %>% 
    glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial(link = "logit")) 
baltimore_logistic %>% 
  broom::tidy(conf.int = T) %>% 
  mutate(OR = exp(estimate),
         CI_lower = exp(exp(conf.low)),
         CI_upper = exp(exp(conf.high)),
         p_val = rstatix::p_format(p.value, digits = 2)) %>% 
  select(term, OR, CI_lower,CI_upper, p_val) %>% 
  mutate(term = str_replace(term, "victim_age", "Victim age"),
         term = str_replace(term, "victim_race", "Victim Race: "),
         term = str_replace(term, "victim_sex", "Victim Sex: ")) %>% 
  knitr::kable(digits = 3, align = "lccc", 
               col.names = c("Term", "Estimated adjusted OR", "CI lower bound", "CI upper bound", "p-value"))
```

* In Baltimore, MD, controlling for all other variables, the homicides whose victim is male are significantly less like to be resolved than those whose victim is female.

```{r, warning=FALSE, message=FALSE}
#  Extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims from all the cities.
allcities_logistic = homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = map(data, ~glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial(link = "logit"))),
    results = map(models, ~broom::tidy(.x, conf.int = T))) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(conf.low),
    CI_upper = exp(conf.high),
    p_val = rstatix::p_format(p.value, digits = 2)
  ) %>% 
  filter(term == "victim_sexMale") %>% 
  select(city_state, OR, CI_lower,CI_upper, p_val) 
allcities_logistic %>% 
  knitr::kable(digits = 3, align = "llccc", col.names = c("City", "Estimated adjusted OR", "CI lower bound", "CI upper bound", "p-value"))
```
```{r, warning=FALSE, message=FALSE}
# Create a plot showing the estimated ORs and CIs for each city
allcities_logistic %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>%
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(x = "City", y = "Estimated OR with CI")
```

## Problem 3
```{r, message=FALSE}
birthweight = read_csv("./birthweight.csv")
```

### Data Preprocessing

```{r}
birthweight_tidy =
  birthweight %>% 
  janitor::clean_names() %>%
  mutate(across(.cols = c(babysex, frace, malform, mrace), as.factor)) %>%
  mutate(babysex = case_when(babysex == 1 ~"male", babysex == 2 ~"female"),
         malform = case_when(malform == 0 ~"absent", malform == 1 ~ "present"),
         frace = recode(frace, 
                        "1" = "White", 
                        "2" = "Black", 
                        "3" = "Asian", 
                        "4" = "Puerto Rican", 
                        "8" = "Other", 
                        "9" = "Unknown"),
         mrace = recode(mrace, 
                        "1" = "White", 
                        "2" = "Black", 
                        "3" = "Asian", 
                        "4" = "Puerto Rican", 
                        "8" = "Other"))
# check missing values
sum(is.na(birthweight_tidy))
```

```{r, message=FALSE}
#Propose a Regression Model for Birthweight.First, I use stepwise method to select variables.
mult_fit = lm(bwt ~ ., data=birthweight_tidy)
step(mult_fit, direction="both")
```

After stepwise selection, I get `babysex`, `bhead`, `blength`, `delwt`, `fincome`, `gaweeks`, `mheight`, `mrace`, `parity`, `ppwt` and `smoken` left in the model.

```{r}
mult_fit_1 = lm(bwt ~  babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken,
              data=birthweight_tidy)
summary(mult_fit_1)
```

Second, I would like to explore the collinearity among these selected continuous variables.

```{r, message=FALSE, warning=FALSE}
fit_var = birthweight_tidy %>%
  select(bhead, blength, delwt, fincome, gaweeks, mheight, parity, ppwt, smoken)
# Correlation matrix for all selected continuous variables
cor(fit_var)
# Scatter plot matrix for all selected continuous variables
pairs(fit_var)
```

From the plot above, we can observe that the a potential collinearity might exsit between `delwt` and `ppwt`, as well as `bhead` and `blength`. Therefore, I plan to drop `ppwt` and `blength` whose p-values are relatively larger in my model.

```{r}
# my model
mult_fit_2 = lm(bwt ~  babysex + bhead + delwt + fincome + gaweeks + mheight + mrace + parity + smoken,
              data=birthweight_tidy)
summary(mult_fit_2)
```

Next, I will show a plot of model residuals against fitted values.

```{r, message=FALSE}
birthweight_tidy %>%
  add_residuals(mult_fit_2) %>%
  add_predictions(mult_fit_2) %>%
  ggplot(aes(x = pred, y = resid)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Plot of the Model Residuals Against Fitted Values",
       x = "Fitted Values", y = "Residuals") 
```

From the plot of residuals against fitted values above, we can observe a cluster around 0, and some extreme values when prediction is below 1000. The constant variance assumption is generally satisfied.
